\begin{abstract}
\noindent
Climate and weather data are the main sources to determine plots for specific plants or plant species for a specific climate. Because of that, farmers need to know the climate and weather data to optimize their work. Swiss farmers have the advantage of getting this information through a federal agency, which does not apply to farmers in subtropical areas. To provide these information for farmers in subtropical areas, a low-priced mobile weather station is required. This project should design a prototype of a weather station, which can record data for air temperature, Rainfall, wind strength and hours of sunshine. In addition to that, the DS3231 real time clock (RTC) should generate a timestamp to the data before it is stored in the data memory. The core of the weather station is the microcontroller ArduinoMega2560, which contains the program code and manages the data storage. The wind strength is being measured by the WD123 from Froggit, the rainfall by an ombrometer from Misol and the air temperature by the BME280 from Bosch that measures also humidity and pressure of the air. Moreover, a wind vane (p/n 80422) from Argent Data Systems allows the weather station to determine the wind direction. Those gained data points are stored on an internal microSD card.\\[0.5cm]
The mobile weather station is able to provide data for temperature, humidity and pressure of the air as well as the Rainfall and the strength and direction of the wind. Furthermore, the mobile weather station is also able to store the data points with timestamp on the microSD card. In a further project, a battery will be implemented which will be supported by photovoltaic. Furthermore, GPS and data query over SMS (GSM) will also be implemented in that further project.\\
\\
Key Words: mobile weather station, sensors, microSD card, GPS, SMS (GSM)


\end{abstract}	